---
title: "CROP RECOMMENDATION"
output:
  flexdashboard::flex_dashboard
runtime: shiny
---

# Table

```{r}
library(DT)
startData <- read.csv("Crop_recommendation.csv")
DT::datatable(startData)
```


# Analysis

## Column {.sidebar}

```{r}


  output$summary1 <- renderPrint({
    if(input$datalist=="All"){
      myVec2=c()
      val <- 2
      while(val <= row_num){
        myVec2 <- append(myVec2,mean(t(data_origin[val,])))
        val<-val+1
      }
      summary(myVec2)
    }
    else{
      label <- input$datalist
      rows <- length(t(data_origin[,2]))
      summary(data_origin[2:rows,label])
    }
  })
  
  
  output$standD <- renderText({
    if(input$datalist=="All"){
      myVec2=c()
      val <- 2
      while(val <= row_num){
        myVec2 <- append(myVec2,mean(t(data_origin[val,])))
        val<-val+1
      }
      c("Standard Deviation: ",sd(myVec2))
    }
    else{
      label <-input$datalist
      rows <- length(t(data_origin[,2]))
      c("Standard Deviation: ",sd(data_origin[2:rows,label]))
    }
  })
  
output$IQR <- renderText({
    if(input$datalist=="All"){
      myVec2=c()
      val <- 2
      while(val <= row_num){
        myVec2 <- append(myVec2,mean(t(data_origin[val,])))
        val<-val+1
      }
      c("IQR: ",IQR(myVec2))
    }
    else{
      label <-input$datalist
      rows <- length(t(data_origin[,2]))
      c("IQR: ",IQR(data_origin[2:rows,label]))
    }
  })
data <- read.csv("Crop_recommendation.csv")
data_origin <- subset(data, select = -c(8,8))
selectInput("datalist", "Choose a column:", c(rownames(t(data_origin))))
```
## Column

```{r}
column(8, verbatimTextOutput("minval"))
column(8, verbatimTextOutput("maxval"))
column(8, verbatimTextOutput("summary1"))
column(8, verbatimTextOutput("standD"))
column(8, verbatimTextOutput("IQR"))
```


# Regression Analysis
## ph~Rainfall
Regression analysis of "rainfall" with "ph"
```{r}

library(datasets)
mydata=as.data.frame(read.csv("Crop_recommendation.csv"))
colnames(mydata)=c("N", "P", "K", "temperature", "humidity", "ph", "rainfall")
model1=lm(ph~rainfall, data=mydata)
plot(ph~rainfall, data=mydata,
      xlab="rainfall", ylab="ph")
abline(model1)
```

## ph~humidity
Regression analysis of "Humidity" with "ph"
```{r}

library(datasets)
mydata=as.data.frame(read.csv("Crop_recommendation.csv"))
colnames(mydata)=c("N", "P", "K", "temperature", "humidity", "ph", "rainfall")
model1=lm(ph~humidity, data=mydata)
plot(ph~humidity, data=mydata,
      xlab="humidity", ylab="ph")
abline(model1)
```

## N~ph
Regression analysis of "ph" with "N"
```{r}

library(datasets)
mydata=as.data.frame(read.csv("Crop_recommendation.csv"))
colnames(mydata)=c("N", "P", "K", "temperature", "humidity", "ph", "rainfall")
model1=lm(N~ph, data=mydata)
plot(N~ph, data=mydata,
      xlab="ph", ylab="N")
abline(model1)
```

## P~ph
Regression analysis of "ph" with "P"
```{r}

library(datasets)
mydata=as.data.frame(read.csv("Crop_recommendation.csv"))
colnames(mydata)=c("N", "P", "K", "temperature", "humidity", "ph", "rainfall")
model1=lm(P~ph, data=mydata)
plot(P~ph, data=mydata,
      xlab="ph", ylab="P")
abline(model1)
```

## K~ph
Regression analysis of "ph" with "K"
```{r}

library(datasets)
mydata=as.data.frame(read.csv("Crop_recommendation.csv"))
colnames(mydata)=c("N", "P", "K", "temperature", "humidity", "ph", "rainfall")
model1=lm(K~ph, data=mydata)
plot(K~ph, data=mydata,
      xlab="ph", ylab="K")
abline(model1)
```




# Histogram

```{r setup, include=FALSE}
library(tidyverse)
library(DT)
startData <- read.csv("Crop_recommendation.csv")
updateData <- reactive(
startData %>% group_by(!!! rlang::syms(input$GB)) %>%
summarise_if(is.numeric,sum,na.rm=T))
```

## Column {.sidebar}

```{r}
selectInput(inputId = "GB",label= "Group By", choices = names(startData))
selectInput(inputId = "Metric",label= "Metric", choices = 
names (select_if(startData, is.numeric)))
```

## Column

### Histogram

```{r}
renderPlot({
  updateData()%>% 
    ggplot(aes(x=!! rlang::sym(input$GB),y=!! rlang::sym(input$Metric),fill=!!
rlang::sym(input$GB))) +
    geom_col()
})
```

### Table

```{r}
renderDT(
  updateData(), rownames = F, extensions = 'Buttons', filter="top", editable=T,
  options = list(
    dom = 'Blfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
    lengthMenu = list(c(10,50, 100, -1), c(10,50, 100, "All"))
  )
)
```


# Edit Table


```{r}
library(DT)
startData <- read.csv("Crop_recommendation.csv", header = TRUE, sep = ",")
DT::datatable(startData)
var1 <- renderDT(
  updateData(), rownames = F, extensions = 'Buttons', filter="top", editable=T,
  options = list(
    dom = 'Blfrtip',
    buttons = c('Insert', 'Delete'),
    lengthMenu = list(c(10,50), c(10,50))
  )
)
edit(startData)
```


# Distributions

```{r}
library(tidyverse)
library(DT)
sData <- read.csv("Crop_recommendation.csv")
uData <- reactive(
sData %>% group_by(!!! rlang::syms(input$GB)) %>%
summarise_if(is.numeric,sum,na.rm=T))
```

## Column {.sidebar}

```{r}
selectInput("Distributions", "Select a Distribution type", choices = c("Normal", "Uniform"))
sliderInput("sampleSize","Select a sample size", min = 0, max = 300, value= 270, step= 0)
conditionalPanel(condition = "input.Distribution == 'Normal'", textInput("Mean", "Please Select Mean", 10), textInput("sd", "Please Select Standard Deviation"))
conditionalPanel(condition = "input.Distribution == 'Uniform'", textInput("u1","Val1: ", value = 1), textInput("u2","Val2: ", value = 1))
server <- function(input, output, session){
output$myPlot <- renderPlot({
distType <- input$Distribution 
size <- input$sampleSize
if(distType == "Normal"){
randomVec <- rnorm(size, mean = as.numeric(input$mean), sd=as.numeric(input$sd))
}
else{
  randomVec <- runif(size, min = 0, max = 300)
}
hist(randomVec, col="blue")})}
```

## Column

### Distribution Plot

```{r}
plotOutput("myPlot")
```
### Table

```{r}
renderDT(
  updateData(), rownames = F, extensions = 'Buttons', filter="top", editable=T,
  options = list(
    dom = 'Blfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
    lengthMenu = list(c(10,50, 100, -1), c(10,50, 100, "All"))
  )
)
```

